### 2021-04-09 ch04_papers_ecs_tcr_assessment/papers_ecs_tcr_assessment.tex
Further style optimization
Replaced appearances of 'circle' with 'point'

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/gregory_regression_cmip6_mmm.pdf}
  \caption[
    Gregory regression for the \acs{CMIP}6 \acl{MMM}.
  ]{
    Gregory regression for the \acs{CMIP}6 \acf{MMM} following
    \textcite{Gregory2004}: Global and annual mean net \acl{TOA} radiation $N$
    versus the change in global and annual mean \acl{T} $\Delta T$ for 150
    years of a simulation with an abrupt quadrupling of the atmospheric
    \acs{CO2} concentration (\nxcotwo{4}) for the \acs{CMIP}6 \acs{MMM}
    (circles). To account for energy leakage and model drift, a linear fit of
    the corresponding pre-industrial control run is subtracted from the
    \nxcotwo{4} simulation. A linear regression can be used to calculate the
    \acf{ECS} according to \cref{eq:02:ecs} with the radiative forcing
    $F_\mathtxt{4x}$ (\yintercept) and the climate feedback parameter $\lambda$
    (slope) for all 150 years (black line), which results in $\mathtxt{ECS} =
    3.74 \unit{K}$. Due to non-linear effects, the exact value of \acs{ECS}
    depends on the years considered for the Gregory regression (see
    \cref{subsec:02:ecs} and \cref{fig:02:gregory_regression_different_years}):
    Using only the first 20 years of the simulation (blue circles and line)
    yields a considerably smaller \acs{ECS} than using only the last 130 years
    of the simulation (orange circles and line). \AdaptedFrom{Meehl2020}.
  }
  \label{fig:04:gregory_regression_cmip6_mmm}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/historical_ecs_tcr_ranges.pdf}
  \caption[
    Historical values of the \acf{ECS} and the \acf{TCR} for different
    \aclp{AR} and climate model ensembles.
  ]{
    Assessed values of the \acf{ECS} (blue bars) and the \acf{TCR} (red bars)
    over the years in the Charney report from 1979 \autocite{Charney1979} and
    the subsequent \acfp{AR} of the \acf{IPCC} \autocite{Mitchell1990,
      Kattenberg1996, Albritton2001, Solomon2007, Stocker2013}. Orange and
    green bars represent the modeled ranges of \acs{ECS} and \acs{TCR},
    respectively, from the different climate model ensembles of the \acf{CMIP}
    with the corresponding \acf{MMM} illustrated with the horizontal black
    lines (the green circle represents the output from a single climate
    model). The numbers correspond to individual \acs{CMIP}5 and \acs{CMIP}6
    models (see \cref{tab:04:ecs_tcr_cmip5,tab:04:ecs_tcr_cmip6}).
    \AdaptedFrom{Meehl2020}.
  }
  \label{fig:04:historical_ecs_tcr_ranges}
\end{figure}

In contrast to \ac{ECS}, \ac{TCR} has only been evaluated since \acs{AR}1 in
1990, in which it is estimated with $2.3 \unit{K}$ using only a single climate
model \commentcite{Bretherton1990}{see single green circle in
  \cref{fig:04:historical_ecs_tcr_ranges}}. Over the years, the modeled range
of \ac{TCR} has decreased from about $\rangeunit{1.3}{3.8}{K}$ in the
\acs{CMIP}1 models \autocite{Kattenberg1996} to about $\rangeunit{1.1}{2.6}{K}$
in the \acs{CMIP}5 ensemble \autocite{Flato2013}. Similarly, the assessed range
of \ac{TCR}, which was first quoted in \acs{AR}4 with $\rangeunit{1.0}{3.0}{K}$
\autocite{Solomon2007}, has been reduced to $\rangeunit{1.0}{2.5}{K}$ in the
subsequent \acs{AR}5 \autocite{Stocker2013}. While the corresponding climate
model ranges from \acs{CMIP}3 and \acs{CMIP}5 agree with these assessed ranges
\autocite{Randall2007, Flato2013}, the upper bound of the \acs{CMIP}6 model
range ($\rangeunit{1.3}{3.0}{K}$) is well above the assessed upper bound of
$2.5 \unit{K}$ given by \acs{AR}5. However, unlike \ac{ECS}, also the lower
bound of the \acs{CMIP}6 model range increased compared to the \acs{CMIP}5
ensemble, leading to a similar \ac{TCR} model spread in both climate model
generations. Due to the correlation of \ac{TCR} and \ac{ECS} given by
\cref{eq:02:tcr_vs_ecs}, the increase of \ac{TCR} in many \acs{CMIP}6 models is
not surprising in light of the many high \ac{ECS} models that are present in
the \acs{CMIP}6 ensemble.

@@

Various improvements of the underlying physical, biological, and chemical
processes have been introduced to the \acs{CMIP}6 \acp{ESM} to represent the
coupled Earth system in more detail. Since many of these processes directly
influence the models' \ac{ECS} \autocite{Forster2020}, determining reasons for
the increased \ac{ECS} in the \acs{CMIP}6 ensemble is highly non-trivial. As
discussed in detail by \textcite{Meehl2020}, one possible reason is the
consideration of aerosol-cloud interactions. New prognostic aerosol schemes
added to some \acs{CMIP}6 models that include aerosol-cloud interactions could
have produced overly large negative radiative forcing, which then required a
stronger model response to \ac{GHG} forcing to reproduce the observed
historical temperature trend. In fact, \textcite{Meehl2020} find a weak
inter-model relationship between the aerosol forcing and \ac{ECS} for some
\acs{CMIP}6 models, with larger negative present-day aerosol forcing associated
with higher \ac{ECS}. Such relationships have also been found for previous
climate model generations \autocite{Kiehl2007, Forster2013}. However, due to
the varying aerosol forcing over time, these relations cannot be used to tune
\ac{ECS} based on the models' responses to aerosols over the different periods
of the \nth{20} century \autocite{Dittus2020}. Further aerosol-cloud
interactions that are relevant in the context of high climate sensitivity in
\acs{CMIP}6 are found for example in the \ac{HadGEM} Version 3. The new aerosol
scheme in this model suppresses a strong negative cloud feedback over the
Southern Ocean that is found in the model's predecessor versions
\autocite{BodasSalcedo2019}. The Southern Ocean is one of the most pristine
aerosol regions in the world \autocite{Hamilton2014}, where aerosols
predominantly originate from natural sources like marine emissions of gaseous
dimethyl sulfide. Earlier \ac{HadGEM} versions show a large reduction in cloud
droplet size with warming over the Southern Ocean, which increases the cloud
albedo and thus produces a negative shortwave cloud feedback. On the contrary,
in \acs{HadGEM}3, this negative feedback is completely suppressed or even
positive due to a small increase of the cloud droplet size with warming, which
eventually increases \ac{ECS} due to an increased net cloud feedback
\autocite{BodasSalcedo2019}.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/gregory_regression_cmip6_mmm.pdf}
  \caption[
    Gregory regression for the \acs{CMIP}6 \acl{MMM}.
  ]{
    Gregory regression for the \acs{CMIP}6 \acf{MMM} following
    \textcite{Gregory2004}: Global and annual mean net \acl{TOA} radiation $N$
    versus the change in global and annual mean \acl{T} $\Delta T$ for 150
    years of a simulation with an abrupt quadrupling of the atmospheric
    \acs{CO2} concentration (\nxcotwo{4}) for the \acs{CMIP}6 \acs{MMM}
    (points). To account for energy leakage and model drift, a linear fit of
    the corresponding pre-industrial control run is subtracted from the
    \nxcotwo{4} simulation. A linear regression can be used to calculate the
    \acf{ECS} according to \cref{eq:02:ecs} with the radiative forcing
    $F_\mathtxt{4x}$ (\yintercept) and the climate feedback parameter $\lambda$
    (slope) for all 150 years (black line), which results in $\mathtxt{ECS} =
    3.74 \unit{K}$. Due to non-linear effects, the exact value of \acs{ECS}
    depends on the years considered for the Gregory regression (see
    \cref{subsec:02:ecs} and \cref{fig:02:gregory_regression_different_years}):
    Using only the first 20 years of the simulation (blue points and line)
    yields a considerably smaller \acs{ECS} than using only the last 130 years
    of the simulation (orange points and line). \AdaptedFrom{Meehl2020}.
  }
  \label{fig:04:gregory_regression_cmip6_mmm}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/historical_ecs_tcr_ranges.pdf}
  \caption[
    Historical values of the \acf{ECS} and the \acf{TCR} for different
    \aclp{AR} and climate model ensembles.
  ]{
    Assessed values of the \acf{ECS} (blue bars) and the \acf{TCR} (red bars)
    over the years in the Charney report from 1979 \autocite{Charney1979} and
    the subsequent \acfp{AR} of the \acf{IPCC} \autocite{Mitchell1990,
      Kattenberg1996, Albritton2001, Solomon2007, Stocker2013}. Orange and
    green bars represent the modeled ranges of \acs{ECS} and \acs{TCR},
    respectively, from the different climate model ensembles of the \acf{CMIP}
    with the corresponding \acf{MMM} illustrated with the horizontal black
    lines (the green point represents the output from a single climate model).
    The numbers correspond to individual \acs{CMIP}5 and \acs{CMIP}6 models
    (see \cref{tab:04:ecs_tcr_cmip5,tab:04:ecs_tcr_cmip6}).
    \AdaptedFrom{Meehl2020}.
  }
  \label{fig:04:historical_ecs_tcr_ranges}
\end{figure}

In contrast to \ac{ECS}, \ac{TCR} has only been evaluated since \acs{AR}1 in
1990, in which it is estimated with $2.3 \unit{K}$ using only a single climate
model \commentcite{Bretherton1990}{see single green point in
  \cref{fig:04:historical_ecs_tcr_ranges}}. Over the years, the modeled range
of \ac{TCR} has decreased from about $\rangeunit{1.3}{3.8}{K}$ in the
\acs{CMIP}1 models \autocite{Kattenberg1996} to about $\rangeunit{1.1}{2.6}{K}$
in the \acs{CMIP}5 ensemble \autocite{Flato2013}. Similarly, the assessed range
of \ac{TCR}, which was first quoted in \acs{AR}4 with $\rangeunit{1.0}{3.0}{K}$
\autocite{Solomon2007}, has been reduced to $\rangeunit{1.0}{2.5}{K}$ in the
subsequent \acs{AR}5 \autocite{Stocker2013}. While the corresponding climate
model ranges from \acs{CMIP}3 and \acs{CMIP}5 agree with these assessed ranges
\autocite{Randall2007, Flato2013}, the upper bound of the \acs{CMIP}6 model
range ($\rangeunit{1.3}{3.0}{K}$) is well above the assessed upper bound of
$2.5 \unit{K}$ given by \acs{AR}5. However, unlike \ac{ECS}, also the lower
bound of the \acs{CMIP}6 model range increased compared to the \acs{CMIP}5
ensemble, leading to a similar \ac{TCR} model spread in both climate model
generations. Due to the correlation of \ac{TCR} and \ac{ECS} given by
\cref{eq:02:tcr_vs_ecs}, the increase of \ac{TCR} in many \acs{CMIP}6 models is
not surprising in light of the many high \ac{ECS} models that are present in
the \acs{CMIP}6 ensemble.

@@

Various improvements of the underlying physical, biological, and chemical
processes have been introduced to the \acs{CMIP}6 \acp{ESM} to represent the
coupled Earth system in more detail. Since many of these processes directly
influence the models' \ac{ECS} \autocite{Forster2020}, determining reasons for
the increased \ac{ECS} in the \acs{CMIP}6 ensemble is highly non-trivial. As
discussed in detail by \textcite{Meehl2020}, one possible reason is the
consideration of aerosol-cloud interactions. New prognostic aerosol schemes
added to some \acs{CMIP}6 models that include aerosol-cloud interactions could
have produced overly large negative radiative forcing, which then required a
stronger model response to \ac{GHG} forcing to reproduce the observed
historical temperature trend. In fact, \textcite{Meehl2020} find a weak
inter-model relationship between the aerosol forcing and \ac{ECS} for some
\acs{CMIP}6 models, with larger negative present-day aerosol forcing associated
with higher \ac{ECS}. Such relationships have also been found for previous
climate model generations \autocite{Kiehl2007, Forster2013}. However, due to
the varying aerosol forcing over time, these relations cannot be used to tune
\ac{ECS} based on the models' responses to aerosols over the different periods
of the \nth{20} century \autocite{Dittus2020}. Further aerosol-cloud
interactions that are relevant in the context of high climate sensitivity in
\acs{CMIP}6 can be found, for example, in the \ac{HadGEM} Version 3. The new
aerosol scheme in this model suppresses a strong negative cloud feedback over
the Southern Ocean that is found in the model's predecessor versions
\autocite{BodasSalcedo2019}. The Southern Ocean is one of the most pristine
aerosol regions in the world \autocite{Hamilton2014}, where aerosols
predominantly originate from natural sources like marine emissions of gaseous
dimethyl sulfide. Earlier \ac{HadGEM} versions show a large reduction in cloud
droplet size with warming over the Southern Ocean, which increases the cloud
albedo and thus produces a negative shortwave cloud feedback. On the contrary,
in \acs{HadGEM}3, this negative feedback is completely suppressed or even
positive due to a small increase of the cloud droplet size with warming, which
eventually increases \ac{ECS} due to an increased net cloud feedback
\autocite{BodasSalcedo2019}.

### 2021-04-09 ch05_paper_ecs/paper_ecs.tex
Replaced appearances of 'circle' with 'point'

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:f}
  \end{subfigure}
  \caption[
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 and
    \acs{CMIP}6 ensemble.
  ]{
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 (blue)
    and \acs{CMIP}6 ensemble (orange). (a), (c), (e) Emergent relationships
    (solid lines) for the \acs{CMIP} models (numbers; see
    \cref{tab:app:a:cmip5_emergent_constraints_part1,%
      tab:app:a:cmip6_emergent_constraints_part1} for details) with their
    \aclp{SPE} (blue and orange shaded areas; see \cref{eq:02:spe}). The
    vertical dashed line corresponds to the observational reference with its
    standard error (gray shaded area). The horizontal dashed lines show the
    best estimates of the constrained \acf{ECS}, and the colored circles mark
    the \aclp{MMM} for \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange). (b), (d),
    (f) \Aclp{PDF} for \acs{ECS} of the emergent constraints (solid lines;
    see \cref{eq:02:pdf_y_given_x0}) and the unconstrained model ensembles
    (histograms). Due to the availability of data, the histograms may differ
    for the different emergent constraints. \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:bri_cox_lip}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{ch05_paper_ecs/figs/zha.pdf}
  \caption[
    Emergent relationship ZHA for different subsets of \acs{CMIP}5 models.
  ]{
    Emergent relationship ZHA \autocite{Zhai2015} for different subsets of
    \acs{CMIP}5 models. Blue circles show the 15 \acs{CMIP}5 models used in the
    original publication (except for \acs{CESM}1-CAM5). The solid blue line and
    blue shaded area show the emergent relationships evaluated on these models
    including the uncertainty range. In our study, we added 11 more \acs{CMIP}5
    models (red circles). The corresponding emergent relationship that
    considers all available \acs{CMIP}5 models is shown in red colors. This
    relationship shows a considerably lower coefficient of determination
    ($R^2$) and higher $p$-value than the relationship using the original
    subset of \acs{CMIP}5 models. The vertical dashed line and shaded area
    correspond to the observational reference, and the horizontal dashed lines
    show the corresponding constraints on the \acf{ECS} using this observation.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:zha}
\end{figure}

@@

In this \lcnamecref{ch:05:paper_ecs}, 11 different emergent constraints on
\ac{ECS}, which are mostly directly or indirectly related to cloud feedbacks,
are assessed by applying them to results from \acp{ESM} contributing to
\acs{CMIP}5 and \acs{CMIP}6. Of particular interest are the results from
\acs{CMIP}6, since all analyzed emergent constraints have been published prior
to the availability of \acs{CMIP}6 data. In summary, the best estimate of
\ac{ECS} averaged over all emergent constraints increases by $12 \unit{\%}$
when moving from relationships trained on \acs{CMIP}5 to those trained on
\acs{CMIP}6. Some increase is predicted by almost every constraint we analyze
(with TII as the only exception) and can at least be partly explained by the
increased multi-model mean \ac{ECS} of \acs{CMIP}6, which has not been
accompanied by systematic changes in the constraint variables that could
explain this increase, leading to regression fits with higher intercept values
at observed constraint values. This is also illustrated by the \acs{CMIP}5 and
\acs{CMIP}6 \acp{MMM} in the left columns of
\cref{fig:05:bri_cox_lip,fig:05:shd_shl_shs,fig:05:su_tih_tii,fig:05:vol_zha}
(colored circles), in which the connecting line between the \acs{CMIP}5 and
\acs{CMIP}6 \ac{MMM} is not parallel to the \acs{CMIP}5 emergent relationships
for all emergent constraints.

>>>>

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:f}
  \end{subfigure}
  \caption[
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 and
    \acs{CMIP}6 ensemble.
  ]{
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 (blue)
    and \acs{CMIP}6 ensemble (orange). (a), (c), (e) Emergent relationships
    (solid lines) for the \acs{CMIP} models (numbers; see
    \cref{tab:app:a:cmip5_emergent_constraints_part1,%
      tab:app:a:cmip6_emergent_constraints_part1} for details) with their
    \aclp{SPE} (blue and orange shaded areas; see \cref{eq:02:spe}). The
    vertical dashed line corresponds to the observational reference with its
    standard error (gray shaded area). The horizontal dashed lines show the
    best estimates of the constrained \acf{ECS}, and the colored points mark
    the \aclp{MMM} for \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange). (b), (d),
    (f) \Aclp{PDF} for \acs{ECS} of the emergent constraints (solid lines;
    see \cref{eq:02:pdf_y_given_x0}) and the unconstrained model ensembles
    (histograms). Due to the availability of data, the histograms may differ
    for the different emergent constraints. \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:bri_cox_lip}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{ch05_paper_ecs/figs/zha.pdf}
  \caption[
    Emergent relationship ZHA for different subsets of \acs{CMIP}5 models.
  ]{
    Emergent relationship ZHA \autocite{Zhai2015} for different subsets of
    \acs{CMIP}5 models. Blue points show the 15 \acs{CMIP}5 models used in the
    original publication (except for \acs{CESM}1-CAM5). The solid blue line and
    blue shaded area show the emergent relationships evaluated on these models
    including the uncertainty range. In our study, we added 11 more \acs{CMIP}5
    models (red points). The corresponding emergent relationship that considers
    all available \acs{CMIP}5 models is shown in red colors. This relationship
    shows a considerably lower coefficient of determination ($R^2$) and higher
    $p$-value than the relationship using the original subset of \acs{CMIP}5
    models. The vertical dashed line and shaded area correspond to the
    observational reference, and the horizontal dashed lines show the
    corresponding constraints on the \acf{ECS} using this observation.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:zha}
\end{figure}

@@

In this \lcnamecref{ch:05:paper_ecs}, 11 different emergent constraints on
\ac{ECS}, which are mostly directly or indirectly related to cloud feedbacks,
are assessed by applying them to results from \acp{ESM} contributing to
\acs{CMIP}5 and \acs{CMIP}6. Of particular interest are the results from
\acs{CMIP}6, since all analyzed emergent constraints have been published prior
to the availability of \acs{CMIP}6 data. In summary, the best estimate of
\ac{ECS} averaged over all emergent constraints increases by $12 \unit{\%}$
when moving from relationships trained on \acs{CMIP}5 to those trained on
\acs{CMIP}6. Some increase is predicted by almost every constraint we analyze
(with TII as the only exception) and can at least be partly explained by the
increased multi-model mean \ac{ECS} of \acs{CMIP}6, which has not been
accompanied by systematic changes in the constraint variables that could
explain this increase, leading to regression fits with higher intercept values
at observed constraint values. This is also illustrated by the \acs{CMIP}5 and
\acs{CMIP}6 \acp{MMM} in the left columns of
\cref{fig:05:bri_cox_lip,fig:05:shd_shl_shs,fig:05:su_tih_tii,fig:05:vol_zha}
(colored points), in which the connecting line between the \acs{CMIP}5 and
\acs{CMIP}6 \ac{MMM} is not parallel to the \acs{CMIP}5 emergent relationships
for all emergent constraints.
